COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2020-04-22 main.tex
Clean up normalization of PDFs in later figures, add more captions

\begin{figure*}
    \includegraphics[width=\textwidth]{figures/coll_hist_e_and_m.png}
    \caption{Caption goes here.\label{fig:coll_hist_e_and_m}}
\end{figure*}

\begin{figure*}
    \begin{center}
    \includegraphics[width=\textwidth]{figures/coll_hist_hot_cold_a.png}
    \caption{Caption goes here.\label{fig:coll_hist_hot_cold_a}}
    \end{center}
\end{figure*}

\begin{figure*}
    \begin{center}
    \includegraphics[width=0.4\textwidth]{figures/coll_gf_vary.png}
    \caption{Caption goes here.\label{fig:coll_gf_varg}}
    \end{center}
\end{figure*}

\begin{figure*}
    \begin{center}
    \includegraphics[width=\textwidth]{figures/coll_hist_r_inout_res.png}
    \caption{Caption goes here.\label{fig:coll_hist_r_inout_res}}
    \end{center}
\end{figure*}

\begin{figure*}
    \begin{center}
    \includegraphics[width=\textwidth]{figures/wander_res_scale.png}
    \caption{Caption goes here.\label{fig:wander_res_scale}}
    \end{center}
\end{figure*}

>>>>

\begin{figure*}
    \includegraphics[width=\textwidth]{figures/coll_hist_e_and_m.png}
    \caption{\textit{Top}: KDE of the number of collisions at each semimajor axis (left) and heliocentric distance (right) as the eccentricity of of the perturbing planet is varied. \textit{Bottom}:  Same as top row, except the perturber's eccentricity is set to $e_{jup}$ and the mass is now varied. In all plots, the PDF is normalized to the ($e_{jup}, m_{jup}$) case. Characteristic bumps or dips appear near the 2:1 and 3:1 MMRs, the presence of which depends on the mass and eccentricity of the perturber. \label{fig:coll_hist_e_and_m}}
\end{figure*}

\begin{figure*}
    \begin{center}
    \includegraphics[width=\textwidth]{figures/coll_hist_hot_cold_a.png}
    \caption{KDE of the number of collisions at each semimajor axis for the lowest eccentricity case (left) and highest eccentricity case (right). To elucidate why a bump forms at the 2:1 while a dip forms at the 3:1 MMR, we split the resolved collisions into hot and cold categories. A bump is produced when the hot collision rate increases, while a dip is produced when the cold collision rate decreases.\label{fig:coll_hist_hot_cold_a}}
    \end{center}
\end{figure*}

\begin{figure*}
    \begin{center}
    \includegraphics[width=0.4\textwidth]{figures/coll_gf_vary.png}
    \caption{The collision rate of a population of 300 km planetesimals as a function of the rms eccentricity in the vicinity of the 3:1 and 2:1 MMRs, relative to the value at $\left< e^{1/2} \right>^{2}$ = $10^{-3}$. The resonances will act to dynamically heat the local planetesimal population. The local minimum corresponds to the rms eccentricity at which the typical planetesimal encounter velocity is $v_{esc}$. If the planetesimals are heated by a small amount, gravitational focusing is suppressed and the collision rate decreases. Stronger dynamical heating will increase the encounter rate enough to overcome the lack of gravitational focusing.\label{fig:coll_gf_varg}}
    \end{center}
\end{figure*}

\begin{figure*}
    \begin{center}
    \includegraphics[width=\textwidth]{figures/coll_hist_r_inout_res.png}
    \caption{KDE of the number of collisions at a given heliocentric distance for planetesimals inside (left) and outside (right) of the 2:1 MMR. In the $e_{pl} = 2 e_{jup}$ case, a bump, rather than a dip appears near the 2:1 MMR (see figure \ref{fig:coll_hist_e_and_m}). This bump is produced by non-resonant planetesimals undergoing collisions near the center of the 2:1 MMR.\label{fig:coll_hist_r_inout_res}}
    \end{center}
\end{figure*}

\begin{figure*}
    \begin{center}
    \includegraphics[width=\textwidth]{figures/wander_res_scale.png}
    \caption{The radial excursion distance of a planetesimal $\delta r_{ex}$ =  ($a_{pl} (1 + e_{f}$) (solid lines) near the resonance and full libration width $\delta r_{res}$ (dashed lines) of that resonance for the 3:1 (left) and 2:1 (right) MMR. For the 2:1 MMR, $\delta r_{ex} < \delta r _{res}$ near the resonance for $e_{pl} = 1/2 e_{jup}$ and $e_{pl} = e_{jup}$. In these case, a dip, rather than a bump appears near the resonance in the bottom right panel of figure \ref{fig:coll_hist_e_and_m}. \label{fig:wander_res_scale}}
    \end{center}
\end{figure*}
